---
title: "STAT0029_ICA1"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the data

```{r}
dat <- read.csv("STAT0029_Raw data.csv", header=TRUE)

#change strategy to 1/0
dat$Strategy <- as.factor(ifelse(dat$Strategy=="TFT_C", 0, 1))
dat$Treatment <- as.factor(dat$Treatment)
dat$Human <- as.factor(ifelse(dat$Human=="y", 1, 0))
dat$PD <- as.factor(ifelse(dat$PD=="y", 1, 0))
dat$PDp <- as.factor(ifelse(dat$PDp=="y", 1, 0))
```

Add binary labels, 1=coop, 0=not coop, based on score 

```{r}
dat$Coop <- as.factor(ifelse(dat$Yi>=50, 1, 0))
```

Logistic regression with logit link function (suggest this is preferable as can interpret the logit aspect):

```{r}
log_model_logit <- glm(Coop ~ Treatment*Strategy, data=dat, family=binomial)
summary(log_model_logit)
par(mfrow=c(2,2))
plot(log_model_logit)
```
Logistic regression with probit link function:

```{r}
log_model_probit <- glm(Coop ~ Treatment*Strategy, data=dat, family=binomial(link="probit"))
summary(log_model_probit)
par(mfrow=c(2,2))
plot(log_model_probit)
```


Logistic regression with cloglog link function:

```{r}
log_model_cloglog <- glm(Coop ~ Treatment*Strategy, data=dat, family=binomial(link="cloglog"))
summary(log_model_cloglog)
par(mfrow=c(2,2))
plot(log_model_cloglog)
```



Fitting model with human covar:

```{r}
log_model_human <- glm(Coop ~ Treatment + Strategy + Human, data=dat, family=binomial)
summary(log_model_human)
par(mfrow=c(2,2))
plot(log_model_human)
```



Try some linear models with transformations:

Square root transformation:

```{r}
dat$Ysq <- (dat$Yi)^0.5
```

Fit linear model
```{r}
model_lm <- lm(Ysq ~ Treatment * Strategy, data=dat)
summary(model_lm)
par(mfrow=c(2,2))
plot(model_lm)
```

Angular transform:

```{r}
dat$Yat <- 10*asin(((dat$Yi)/100)^0.5)
```

Fit linear model
```{r}
model_lm_at <- lm(Yat ~ Treatment * Strategy, data=dat)
summary(model_lm_at)
par(mfrow=c(2,2))
plot(model_lm_at)
```